Cluster Dynamics with HETDEX at z < 0.5 - I: Simulated Performance, Mass Distribution and Limits

### 2016-03-15 ms.tex

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. Boada et al.]
{\parbox{\textwidth}{Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
C.~Papovich,$^{1}$
R.~Wechsler,$^{2,3}$
T. S.~Li,$^{1}$
K.~Gebhardt,$^{5}$
E.~Rozo,$^{2,4}$
E. S.~Rykoff$^{2}$}\vspace{0.4cm}\
\\
\parbox{\textwidth}{$^{1}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{4}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
$^{5}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}}

@@

\begin{abstract}
\noindent
The study of clusters of galaxies has been argued to be a very effective way to measure cosmological parameters, including measuring dark energy and testing models of gravity. The Hobby Eberly Telescope Dark Energy Experiment (HETDEX) will observe many hundreds of square degrees, covering a large sample of galaxy clusters to $z < 0.5$ based on their optical spectra ($3500-5500\AAA$). The spectra will provide important measures of the clusters dynamics and may enable constraints on cosmological parameters, but only if the measurements provide accurate estimates of the total cluster masses. We carry out a study to investigate the ability of HETDEX to recover accurate galaxy cluster masses over a wide range of masses and redshifts. We use a detailed mock galaxy catalog and present mock observations of two different scenarios: (1) We targeted individual galaxy clusters to investigate the recovery of parameters with such observations. (2) We created and evaluated a HETDEX-like selection ``function'' of galaxies over a similarly sized portion of the sky and use well adopted techniques to recover the dynamical properties, such as velocity dispersion and mass, and benchmark these against observations with perfect knowledge. Using both observing strategies, we produce cluster mass probability density functions $P(M|z, X)$, which can be used to determine the probability that a galaxy cluster of given mass (M), located at redshift ($z$) determined using observable parameter (X). \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations.}
\end{abstract}

@@

Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work. HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, and the upcoming DECam/IRAC Galaxy Environment Survey (DIRGES; PI: Papovich, C. Papovich \etal\ in preparation), the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted). While the potential dataset is very rich, two large issues remain.

@@

\subsection{The ``Buzzard'' Catalogs}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram. See the text for a full description of the process.} \label{fig: oii sdss} 
\end{figure*}

The ``Buzzard'' mock galaxy catalogs (R. Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses and other various parameters.

@@

Tentatively slated to start in the spring of 2016, HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator. The 300 \degsq, spring field and 120 \degsq\ fall field will have no preselected targets. Using VIRUS on the 10-m Hobby-Eberly Telescope \citep{Ramsey1998} the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.

Each mask is created to accurately reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}. The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.

@@

The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729~\AAA$ doublet) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5~\AAA$) and K ($\lambda 3933.7~\AAA$) absorption features to $z\sim 0.4$. HETDEX is expected to detect sources with continuum brighter than $\sdssg=22$ mag, and emission line strengths above $3.5\times10^{-17}$ \ergscm.

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}
  \label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

@@

\subsection{Other Estimates of Dynamical Mass}
In this section we use two methods to predict the mass of a cluster based on other observables. Often the cluster mass is estimated based on a single observable, X-ray temperature, velocity dispersion, richness and others. Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion. The first method is traditional probability based where we marginalize over a series of observables to find the most probable mass. The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass. Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the mass) are both known.

@@

\subsubsection{Probability Based}\label{sec:probability method}
We begin with the training sample. After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass (M) and $\vec{x}$. Because $\vec{x}$ can be multidimensional, we rely on the ``corner plot'' as an aid to visualize the relationship between all of the training features. Figure~\ref{fig: probability corner}, a corner plot, shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.

\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/cornertest.pdf} 
	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$. The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass. The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M|\vec{x})$. See text for a complete description. } \label{fig: probability corner} 
\end{figure}

The conditional probability of the mass $P(M|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value. The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$. The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M|\vec{x} = \{ \sigma=400 \kms,z=0.17\})$.

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M)$, we combine the conditional probability distribution, $P(M|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M) = \int P(M|\vec{x}) P(\sigma) d\sigma
\end{equation}
The expected mass is determined by integrating the mass probability, $P(M)$ over all mass. This becomes our ``predicted'' mass, $\langle M\rangle$.
\begin{equation}\label{eq: expected mass}
	\langle M\rangle = \int M^\prime P(M^\prime)dM^\prime
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the variance about the expected mass through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M^\prime - \langle M\rangle)^2 P(M^\prime)dM^\prime
\end{equation}
or by drawing many samples from $P(M)$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.

@@

The prediction intervals here are based on the general method of quantile regression forests \citep{Meinshausen2006}. The general idea is that all response variables are recorded, not just the mean. Then the prediction can be returned as the full conditional probability distribution of all responses, which allows us to generate the prediction intervals. The 68\% prediction interval is determined by calculating the 16th and 84th percentile of the full conditional probability distribution. \editorial{I am going to change this to just the std of the distribution. I need the errorbars to be sysmetric to make the fitting routine easy later on.}

\section{RESULTS}\label{sec:results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies. We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.

\subsection{Recovery of Cluster Members}
As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered. Knowing these limits will provide important information for potential future follow up or targeted observations. In this section we discuss the number of cluster members recovered for both the targeted and survey observation strategies, taking into account all observational limits.

Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass. It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this figure. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.

@@

Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias 
\begin{equation}
\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).\nonumber
\end{equation}
where $y$ is the true value and $\hat{y}$ is the predicted value, and the scatter about the bias
\begin{equation}
	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}\nonumber
\end{equation}
for different bins of cluster mass. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.

@@

For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.37}$ dex and $\mu_{bias} =0.11\pm{0.36}$ dex, respectively. So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average. This does not mean that the survey observations cannot be improved by targeted observations. In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF. The targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.

@@

\caption{Bias and scatter of the true cluster mass for different bins of predicted cluster mass. This table shows the offset and scatter in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}

@@

		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
		&$\sigma$ & $0.87\pm{0.15}$ & $0.53\pm{0.24}$ & $0.32\pm{0.26}$ & $0.16\pm{0.20}$ & $0.10\pm{0.16}$ & $0.07\pm{0.14}$ & $0.05\pm{0.16}$ & $-0.18\pm{0.17}$ \\
		&$\sigma, z$ & $0.76\pm{0.16}$ & $0.42\pm{0.21}$ & $0.17\pm{0.23}$ & $0.01\pm{0.19}$ & $-0.06\pm{0.16}$ & $-0.11\pm{0.55}$ & $-0.14\pm{0.16}$ & $-0.38\pm{0.34}$ \\
		&$\sigma, z, N_{gal}$ & $0.65\pm{0.10}$ & $0.28\pm{0.14}$ & $0.04\pm{0.47}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.05\pm{0.54}$ & $-0.22\pm{1.61}$ & $-6.62\pm{8.08}$ \\

@@

		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.34}$ & $0.28\pm{0.39}$ & $0.23\pm{0.34}$ & $0.16\pm{0.22}$ & $0.11\pm{0.16}$ & $0.07\pm{0.14}$ & $0.02\pm{0.14}$ & $-0.07\pm{0.10}$ \\
		&$\sigma$ & $0.69\pm{0.20}$ & $0.36\pm{0.27}$ & $0.15\pm{0.29}$ & $-0.02\pm{0.24}$ & $-0.07\pm{0.21}$ & $-0.09\pm{0.19}$ & $-0.11\pm{0.18}$ & $-0.12\pm{0.19}$ \\
		&$\sigma, z$ & $0.62\pm{0.18}$ & $0.33\pm{0.22}$ & $0.12\pm{0.25}$ & $-0.01\pm{0.20}$ & $-0.06\pm{0.18}$ & $-0.09\pm{0.16}$ & $-0.11\pm{0.17}$ & $-0.19\pm{0.13}$ \\
		&$\sigma, z, N_{gal}$ & $0.51\pm{0.14}$ & $0.23\pm{0.18}$ & $0.05\pm{0.17}$ & $-0.02\pm{0.14}$ & $-0.02\pm{0.10}$ & $-0.02\pm{0.08}$ & $-0.02\pm{0.08}$ & $-0.08\pm{0.08}$ \\

@@

		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.31}$ & $0.27\pm{0.41}$ & $0.20\pm{0.43}$ & $0.13\pm{0.39}$ & $0.10\pm{0.33}$ & $0.09\pm{0.27}$ & $0.02\pm{0.18}$ & $-0.08\pm{0.09}$ \\
		&$\sigma$ & $1.02\pm{0.13}$ & $0.66\pm{0.19}$ & $0.40\pm{0.24}$ & $0.17\pm{0.25}$ & $0.02\pm{0.25}$ & $-0.08\pm{0.22}$ & $-0.19\pm{0.19}$ & $-0.35\pm{0.26}$ \\

>>>>

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[S. Boada et al.]
{\parbox{\textwidth}{Steven Boada,$^{1}$\thanks{E-mail: boada@physics.tamu.edu}
C.~Papovich,$^{1}$
R.~Wechsler,$^{2,3}$
T. S.~Li,$^{1}$
K.~Gebhardt,$^{5}$
J.~DeRose,$^{2}$
E.~Rozo,$^{2,4}$
E. S.~Rykoff$^{2}$}\vspace{0.4cm}\
\\
\parbox{\textwidth}{$^{1}$George P.\ and Cynthia Woods Mitchell Institute for Fundamental Physics and Astronomy, and Department of Physics and Astronomy, Texas A\&M University, College Station, TX, 77843-4242, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology, Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Menlo Park, CA 94025, USA\\
$^{4}$Department of Physics, University of Arizona, Tucson, AZ 85721, USA\\
$^{5}$Department of Astronomy, The University of Texas at Austin, Austin, TX 78712, USA}}

@@

\begin{abstract}
\noindent
The distribution of massive clusters of galaxies depends strongly on the total cosmic mass density, the mass variance, and the dark energy equation of state. As such, measures of galaxy clusters can provide constraints on these parameters and even test models of gravity, but only if observables of clusters can lead to accurate estimates of their total masses. Here, we carry out a study to investigate the ability of a blind spectroscopic survey to recover accurate galaxy cluster masses through their velocity dispersion. We focus on the Hobby Eberly Telescope Dark Energy Experiment (HETDEX), which will observe many hundreds of square degrees. HETDEX will employ the new VIRUS instrument, an integral field unit (IFU), covering the blue/optical portion of the spectrum (3500--5500~\AAA) blindly in two fields for a total of 420 \degsq\ on the sky with fibers with a 1/4.5 fill factor. This allows surveys with VIRUS to measure redshifts for a large sample of galaxies out to $z < 0.5$ based on their absorption features or [\ion{O}{ii}] $\lambda$3727 emission (and Lyman-$\alpha$ over $1.9 < z < 3.5$). We use a detailed mock galaxy catalog from a semi-analytic model to simulate surveys observed with VIRUS, including: (1) a blind, HETDEX-like survey with an incomplete but uniform spectroscopic selection function; and (2) IFU surveys that target clusters directly, obtaining spectra of all galaxies in a VIRUS-sized field. For both surveys, we include realistic uncertainties from galaxy magnitude and line-flux limits. We benchmark both surveys against spectroscopic observations with ``perfect" knowledge of galaxy line-of-sight velocities. Using both observing strategies, we produce cluster mass probability density functions $P(M_{200}|\vec{x})$ of a cluster mass ($M_{200}$) as a function of an observable parameter or set of observable parameters, $\vec{x}$, where we consider cases of where $\vec{x} = \{\sigma\}$, $=\{\sigma, z\}$, and $=\{\sigma,z, N_{gal}\}$ for velocity dispersion, $\sigma$, redshift, and number of observed galaxies, $N_{gal}$. \editorial{This sentence will summarize how well HETDEX will do, and how that might be improved with targeted observations}.
\end{abstract}

@@

Connecting the dynamical properties derived from spectroscopy to the properties inferred from other studies insures the greatest impact on future work. HETDEX overlaps with the Sloan Digital Sky Survey (SDSS; \citealt{Blanton2001a}), SDSS stripe 82 \citep{Annis2014}, DES, the \emph{Spitzer}/HETDEX Exploratory Large-Area Survey (SHELA; Papovich \etal\ 2016, ApJS, submitted), and the \emph{Spitzer} IRAC Equatorial Survey (SpIES; Timlin \etal\ 2016, ApJ, submitted). While the potential dataset is very rich, two large issues remain.

@@

\subsection{The Buzzard Mock Catalogs}
\begin{figure*} 
	\includegraphics[width=\textwidth]{figures/oii_sdss.pdf} 
	\caption{\textit{Left}: CMD of 503113 $z<0.2$ galaxies take from the SDSS DR12 where the shading scales with the density of points. The two colored boxes show regions containing potential catalog galaxies. \textit{Right}: Probability histograms of the Log [\ion{O}{ii}] luminosity for the SDSS galaxies located in the two highlighted regions on the right. New [\ion{O}{ii}] luminosity (and subsequently fluxes) are assigned to catalog galaxies from slice sampling the probability histogram. See the text for a full description of the process.} \label{fig: oii sdss} 
\end{figure*}

The Buzzard mock galaxy catalogs (R. Wechsler et al., private communication) cover 398.49 \degsq\ between $4^h< RA < 6^h$ and $-61\degree < DEC < -41\degree$ and are derived from a combination of Sub-halo Abundance Matching (ShAM) and ADDSEDs (Adding Density Dependent Spectral Energy Distributions) tied to an in house n-body cosmological simulation. A brief description of the catalog creation is described as follows. The initial conditions are generated with a second-order Lagrangian perturbation theory using {\tt 2LPTic} \citep{Crocce2006}. Dark matter (DM) n-body simulations are run using {\tt LGadget-2} (a version of {\tt Gadget-2}; \citealt{Springel2005}). The DM halos are identified using the {\tt ROCKSTAR} halo finder \citep{Behroozi2013} which also calculates halo masses.

@@

HETDEX will perform blind spectroscopy (R $\sim$ 750 in $3500 - 5500~\AAA$) over two fields along the celestial equator. The 300 \degsq, spring field and 120 \degsq\ fall field will have no preselected targets. Using VIRUS on the 10-m Hobby-Eberly Telescope \citep{Ramsey1998} the completed survey is expected to have an overall fill-factor of 1/4.5, meaning that the entire area could be covered with 4.5 dithers of the entire survey.

Each mask is created to reproduce the HETDEX IFU pattern, see Figure~\ref{fig: ifu layout}. The pattern consists of 78 IFUs, which are comprised of 448 optical fibers subtending a $50'' \times 50''$ region on the sky \citep{Kelz2014}. The inter-IFU spacing is also $50''$ spanning a total area of $16'\times 16'$ on the sky.

@@

The spectral coverage allows for the detection of [\ion{O}{ii}] ($\lambda\lambda 3727,3729$) emitters to $z\sim 0.5$ and Ca H ($\lambda 3968.5$) and K ($\lambda 3933.7$) absorption features to $z\sim 0.4$. HETDEX is expected to detect sources with continuum brighter than $\sdssg=22$ mag, and emission line strengths above $3.5\times10^{-17}$ \ergscm.

@@

The line-of-sight velocity dispersion (LOSVD) is calculated using a method of maximum likelihood following \cite{Walker2006}. We maximize the probability function 
\begin{equation}\label{eq: jointGaussian}
p(\{v_1, ..., v_N\})=\displaystyle\prod_{i=1}^{N}\frac{1}{\sqrt{2\pi(\sigma_i^2+\sigma_p^2)}}\exp\biggl[-\frac{1}{2}\frac{(v_i-\langle u \rangle)^2}{(\sigma_i^2+\sigma_p^2)}\biggr]
\end{equation}
where $\sigma_p$, $\langle\mu\rangle$, and $\sigma_i$ is the LOSVD, the average radial velocity and the error on the individual LOSVs respectively. Using a Monte Carlo Markov Chain (MCMC) sampler ({\tt emcee}\footnote{\url{http://dan.iel.fm/emcee/current/}}; \citealt{Foreman-Mackey2013}) which is based on affine-invariant ensemble sampler (see \citealt{Goodman2010} for details on affine-invariant samplers). We draw twenty thousand samples from the posterior probability distribution using simple priors, $\langle\mu\rangle$ lies between the maximum and minimum LOSV and $0< \sigma_p < 1400$ \kms. When the full distribution of LOSVDs are not used, the final LOSVD is quoted as the median value of the posterior probability distribution with 68\% error bars defined as the 16th and 84th percentiles of the same distribution.

@@

\subsection{Other Estimates of Dynamical Mass}
In this section we use two methods to predict the mass of a cluster based on other observables. Often the cluster mass is estimated based on a single observable, X-ray temperature, velocity dispersion, richness and others. Here we combine many observables to attempt to correct the mass inferred solely from the velocity dispersion. The first method is traditional probability based where we marginalize over a series of observables to find the most probable mass. The second is based on a machine learning (ML) algorithm which attempts to ``learn'' the relationship between the observables and the desired output, the mass. Both of these methods are examples of supervised learning algorithms where the relationship between the observable parameters and the target parameter (the cluster mass) are both known.

@@

\subsubsection{Probability Based}\label{sec:probability method}
We begin with the training sample. After selecting the desired features $\vec{x} = \{\sigma, z, ...\}$ we make the joint probability between the true cluster mass ($M_{200c}$) and $\vec{x}$. Figure~\ref{fig: probability corner}, a corner plot, shows all of the one (marginalized probability) and two (joint probability) dimensional projections of the posterior probability distributions of the features of the training data.

\begin{figure} 
	\includegraphics[width=\columnwidth]{figures/cornertest.pdf} 
	\caption{Corner plot of the \emph{training} data with features $\sigma$ and $z$. The corner plots shows all of the one and two dimensional posterior probability distributions used to determine the correct cluster mass. The colored rectangles, which have been enlarged for clarity, show the slices needed to create a conditional probability distribution of the mass, $P(M_{200c}|\vec{x})$. See text for a complete description. } \label{fig: probability corner} 
\end{figure}

The conditional probability of the mass $P(M_{200c}|\vec{x}= \{ x_1,x_2,...\})$ is determined by taking a slice through the joint probability distributions in bins centered on the desired value. The slices show by the colored bars in Figure~\ref{fig: probability corner} are centered on $\sigma = 400$ \kms and $z=0.17$. The distribution of mass contained in the three dimensional bin given by the intersection of these slices is $P(M_{200c}|\vec{x} = \{\sigma=400 \kms,z=0.17\})$.

@@

For the clusters making up the \emph{test} sample the mass is unknown (it is what we are trying to predict) but the other features are known. To determine the mass probability distribution of a test cluster, $P(M_{200c})$, we combine the conditional probability distribution, $P(M_{200c}|\vec{x})$, created previously with the probability distribution of $\sigma$ through Equation~\ref{eq: Pm}.
\begin{equation}\label{eq: Pm}
	P(M_{200c}) = \int P(M_{200c}|\vec{x}) P(\sigma) d\sigma
\end{equation}
The expected mass is determined by calculating the first moment of the probability density. This becomes our ``predicted'' mass, $M_{pred}$.
\begin{equation}\label{eq: expected mass}
	M_{pred}= \int M_{200c} P(M_{200c})dM_{200c}
\end{equation}
The confidence interval associated with this prediction can be estimated two ways. First, by calculating the second moment of the probability density through
\begin{equation}\label{eq: variance}
	\mathrm{Var} = \int (M_{200c} - M_{pred})^2 P(M_{200c})dM_{200c}
\end{equation}
or by drawing many samples from $P(M_{200c})$ and calculating the values at the 16th and 84th percentile. In practice we find that both methods produce similar results for a large number of trials. Therefore, we quote predicted masses as the most probable mass given by Equation~\ref{eq: expected mass} and associated 68\% error estimated through Equation~\ref{eq: variance}.

@@

The prediction intervals here are based on the general method of quantile regression forests \citep{Meinshausen2006}. The general idea is that all response variables are recorded, not just the mean. Then the prediction can be returned as the full conditional probability distribution of all responses, which allows us to generate the prediction intervals. The 68\% prediction interval is determined by calculating the 16th and 84th percentile of the full conditional probability distribution. \editorial{I am going to change this to just the std of the distribution. I need the errorbars to be symmetric to make the fitting routine easy later on.}

\section{RESULTS}\label{sec:results}
Here we explore the cluster member recovery rate and mass estimates for the two observing strategies, targeted, and survey. Targeted observations are direct observations of a cluster where each cluster member galaxy, above the detection thresholds (see Section \ref{sec: observations}), is observed. Survey observations mimic the HETDEX observation strategy such that no cluster is directly observed, and only the cluster member galaxies above the detection threshold and within an IFU (see Figure \ref{fig: ifu layout}) are observed.  We discuss the accuracy of dynamical mass derived from both the scaling relation (see Equation \ref{eq:power law}) and through the probability and ML methods.

\subsection{Recovery of Cluster Members}
As discussed in Section \ref{sec: observations} the observational constraints place limits on the total number fo clusters member galaxies expected to be recovered. Knowing these limits will provide important information for potential future follow up or targeted observations. Figure \ref{fig: recovery} shows the recovery fraction of member galaxies, the number of observed galaxies divided by the number of actual galaxies ($N_{obs}/N_{True}$), as function of both redshift and cluster mass. It is important to note that if fewer than five member galaxies are observed ($N_{obs} <5$) the cluster is not considered detected, and is excluded from this figure. As expected, the targeted observing strategy where the individual clusters are targeted through several dithers to ensure near complete coverage, performs significantly better than the survey observing strategy across all redshifts and cluster masses.

@@

Because it represents the best possible scenario, the perfect knowledge observations should serve as baseline to compare the probability based and ML cluster mass recovery methods. And, while there are many possible metrics to evaluate performance, we compute two: the average bias 
\begin{equation}
\mathrm{\mu_{bias}}(y,\hat{y}) = \frac{1}{N} \sum_{i=0}^N (\hat{y_i} - y_i).
\end{equation}
where $y$ is the true value and $\hat{y}$ is the predicted value, and the scatter about the bias
\begin{equation}
	\sigma_{bias}(y,\hat{y}, \mu_{bias}) = \bigg{[}\frac{1}{N-1} \sum_{i=0}^N (\hat{y_i} - y_i - \mu_{bias})^2 \bigg{]}^{1/2}
\end{equation}
for different bins of cluster mass. Both metrics evaluate how closely the ensemble of predicted cluster masses are to the true cluster masses, and in both cases values closer to zero are better.

@@

For the targeted and survey observations the power law predicted cluster masses give $\mu_{bias} =0.13\pm{0.003}$ dex and $\mu_{bias} =0.11\pm{0.009}$ dex, respectively. So for the clusters that we detect with survey observations, we obtain similar levels of accuracy as to the targeted observations, on the average. This does not mean that the survey observations cannot be improved by targeted observations. In fact, when comparing only the galaxies which overlap between the two samples the bias and scatter of the targeted observations is significantly decreased as more cluster member galaxies are detected, better sampling the LOSVD PDF. The targeted observations performs similarly on the average because many lower mass clusters are included in the sample, increasing the bias of the overall sample.

@@

\caption{Bias and scatter of the true cluster mass for different bins of predicted cluster mass. This table shows the bias in the true cluster mass for the perfect (top section), targeted (middle section), and survey (bottom section) observations in different predicted mass bins. The different mass recovery strategies are given in the leftmost column. It can be used to understand how the predicted cluster mass differs from the true cluster masses. Positive numbers indicate the predicted cluster mass over estimates when compared to the true cluster mass.}

@@

		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.09}$ & $0.28\pm{0.02}$ & $0.23\pm{0.01}$ & $0.16\pm{0.00}$ & $0.11\pm{0.00}$ & $0.07\pm{0.00}$ & $0.02\pm{0.01}$ & $-0.07\pm{0.04}$ \\
		&$\sigma$ & $0.87\pm{0.04}$ & $0.53\pm{0.01}$ & $0.32\pm{0.01}$ & $0.16\pm{0.00}$ & $0.10\pm{0.00}$ & $0.07\pm{0.00}$ & $0.05\pm{0.01}$ & $-0.18\pm{0.06}$ \\
		&$\sigma, z$ & $0.76\pm{0.04}$ & $0.42\pm{0.01}$ & $0.17\pm{0.00}$ & $0.01\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.11\pm{0.01}$ & $-0.14\pm{0.01}$ & $-0.38\pm{0.13}$ \\
		&$\sigma, z, N_{gal}$ & $0.65\pm{0.03}$ & $0.28\pm{0.01}$ & $0.04\pm{0.01}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.05\pm{0.01}$ & $-0.22\pm{0.12}$ & $-6.62\pm{3.06}$ \\

@@

		\rottext{4}{ML Based} & Power Law & $0.49\pm{0.09}$ & $0.28\pm{0.02}$ & $0.23\pm{0.01}$ & $0.16\pm{0.00}$ & $0.11\pm{0.00}$ & $0.07\pm{0.00}$ & $0.02\pm{0.01}$ & $-0.07\pm{0.04}$ \\
		&$\sigma$ & $0.69\pm{0.05}$ & $0.36\pm{0.01}$ & $0.15\pm{0.01}$ & $-0.02\pm{0.00}$ & $-0.07\pm{0.00}$ & $-0.09\pm{0.01}$ & $-0.11\pm{0.01}$ & $-0.12\pm{0.07}$ \\
		&$\sigma, z$ & $0.62\pm{0.05}$ & $0.33\pm{0.01}$ & $0.12\pm{0.00}$ & $-0.01\pm{0.00}$ & $-0.06\pm{0.00}$ & $-0.09\pm{0.00}$ & $-0.11\pm{0.01}$ & $-0.19\pm{0.05}$ \\
		&$\sigma, z, N_{gal}$ & $0.51\pm{0.04}$ & $0.23\pm{0.01}$ & $0.05\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.00}$ & $-0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\

@@

		\rottext{4}{Prob Based} & Power Law & $0.49\pm{0.08}$ & $0.27\pm{0.02}$ & $0.20\pm{0.01}$ & $0.13\pm{0.01}$ & $0.10\pm{0.01}$ & $0.09\pm{0.01}$ & $0.02\pm{0.01}$ & $-0.08\pm{0.03}$ \\
		&$\sigma$ & $1.02\pm{0.03}$ & $0.66\pm{0.01}$ & $0.40\pm{0.00}$ & $0.17\pm{0.00}$ & $0.02\pm{0.00}$ & $-0.08\pm{0.01}$ & $-0.19\pm{0.01}$ & $-0.35\pm{0.10}$ \\
